Component response rate variation underlies the stability of highly complex finite systems

### 2020-03-28 notebook/SI.Rmd
Change the SI name so that it fits with Scientific Reports

---
title: "Component response rate variation underlies the stability of highly complex finite systems"
author: "A. Bradley Duthie"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA alexander.duthie@stir.ac.uk
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \usepackage{float}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
subtitle: Supplemental Information
biblio-style: apalike
---

@@

**This supplemental information supports the manuscript "Component response rate variation underlies the stability of complex systems" with additional analyses to support its conclusions. All text, code, and data underlying this manuscript are publicly available on [GitHub](https://github.com/bradduthie/RandomMatrixStability) as part of the RandomMatrixStability R package.**

>>>>

---
title: "Component response rate variation underlies the stability of highly complex finite systems"
author: "A. Bradley Duthie"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA alexander.duthie@stir.ac.uk
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \usepackage{float}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
subtitle: Supplementary Information
biblio-style: apalike
---

@@

**This supplemental information supports the manuscript "Component response rate variation underlies the stability of highly complex finite systems" with additional analyses to support its conclusions. All text, code, and data underlying this manuscript are publicly available on [GitHub](https://github.com/bradduthie/RandomMatrixStability) as part of the RandomMatrixStability R package.**

### 2020-03-28 notebook/SI.tex
Recompile SI files with slight adjustment based on arXiv edits
Change the SI name so that it fits with Scientific Reports

\setlength{\droptitle}{-2em}
  \title{Component response rate variation underlies the stability of highly
complex finite systems}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{Supplemental Information}
  \author{A. Bradley Duthie}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{Biological and Environmental Sciences, University of Stirling, Stirling,
UK, FK9 4LA
\href{mailto:alexander.duthie@stir.ac.uk}{\nolinkurl{alexander.duthie@stir.ac.uk}}}

@@

\textbf{This supplemental information supports the manuscript
``Component response rate variation underlies the stability of complex
systems'' with additional analyses to support its conclusions. All text,
code, and data underlying this manuscript are publicly available on
\href{https://github.com/bradduthie/RandomMatrixStability}{GitHub} as
part of the RandomMatrixStability R package.}

@@

Cascade food webs are more likely to be stable than small-world or
scale-free networks at equivalent magnitudes of complexity (note that
\(C = 1\) for all above rows). A higher number of stable \(\mathbf{M}\)
than \(\mathbf{A}\) was found given \(S \geq 27\).

>>>>

\setlength{\droptitle}{-2em}
  \title{Component response rate variation underlies the stability of highly
complex finite systems}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{Supplementary Information}
  \author{A. Bradley Duthie}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{Biological and Environmental Sciences, University of Stirling, Stirling,
UK, FK9 4LA
\href{mailto:alexander.duthie@stir.ac.uk}{\nolinkurl{alexander.duthie@stir.ac.uk}}}

@@

\textbf{This supplemental information supports the manuscript
``Component response rate variation underlies the stability of highly
complex finite systems'' with additional analyses to support its
conclusions. All text, code, and data underlying this manuscript are
publicly available on
\href{https://github.com/bradduthie/RandomMatrixStability}{GitHub} as
part of the RandomMatrixStability R package.}

@@

Cascade food webs are more likely to be stable than small-world or
scale-free networks at equivalent magnitudes of complexity (note
\(C = 1\) for all above rows). A higher number of stable \(\mathbf{M}\)
than \(\mathbf{A}\) was found given \(S \geq 27\).
